\section{Sok: Research Perspectives and Challenges for Bitcoin and Cryptocurrencies}
\bibentry{bonneau2015research}

\textbf{Abstract:} 
Bitcoin has emerged as the most successful cryptographic currency in history. Within two years of its quiet launch in 2009, Bitcoin grew to comprise billions of dollars of economic value despite only cursory analysis of the system’s design. Since then a growing literature has identified hidden-but-important properties of the system, discovered attacks, proposed promising alternatives, and singled out difficult future challenges. Meanwhile a large and vibrant open-source community has proposed and deployed numerous modifications and extensions. We provide the first systematic exposition Bitcoin and the many related cryptocurrencies or ‘altcoins.’ Drawing from a scattered body of knowledge, we identify three key components of Bitcoin’s design that can be decoupled. This enables a more insightful analysis of Bitcoin’s properties and future stability. We map the design space for numerous proposed modifications, providing comparative analyses for alternative consensus mechanisms, currency allocation mechanisms, computational puzzles, and key management tools. We survey anonymity issues in Bitcoin and provide an evaluation framework for analyzing a variety of privacy-enhancing proposals. Finally we provide new insights on what we term disintermediation protocols, which absolve the need for trusted intermediaries in an interesting set of applications. We identify three general disintermediation strategies and provide a detailed comparison.
